---
title: "HIV Simplification - A target trial emulation"
author: "Bernard Surial"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: true
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r libraries}
# Libraries ---------------------------------------------------------------
library(tidyverse)
library(bernr)
library(here)
library(survminer)
library(survival)
library(ipw)
library(boot)
library(paletteer)
library(patchwork)
library(broom)
library(survey)
library(smd)
library(tableone)
library(gtsummary)
```

```{r theme}
# Functions/Themes ----------------------------------------------------------
theme_set(theme_light(base_family = "Lato"))
theme_update(
  plot.title.position = "plot",
  axis.title.x = element_text(margin = margin(t = 1, unit = "line")),
  axis.title.y = element_text(margin = margin(r = 1, unit = "line")),
  plot.title = element_text(face = "bold", margin = margin(b = 1, unit = "line")),
  strip.background = element_rect(fill = "white"),
  strip.text = element_text(color = "black", face = "bold")
)
```

```{r read_data}
# Read data ---------------------------------------------------------------

df_analysis <- pro_read("05-analysis_data.rds")

# Missing resistance data are coded as "Missing"
df_analysis <- df_analysis %>% 
  mutate(across(c(M184VI, K65R), 
                ~fct_explicit_na(factor(.x, levels = c(TRUE, FALSE), 
                                        labels = c("Yes", "No"))))) %>% 
  mutate(TAMS_nc = fct_explicit_na(factor(TAMS_n))) %>% 
  mutate(log_max_rna = if_else(max_rna > 0, log(max_rna), 0)) %>% 
  mutate(adherence_locf = fct_drop(adherence_locf))


# Separate DF for the outcome "Any HIV > 200" -> can occur before the other 
# outcome, and therefore need to "re-filter"
df_analysis_3 <- df_analysis %>% filter(trial_start < time3_date)


# Censor everyone after 5 years
df_analysis_3 <- df_analysis_3 %>% 
  mutate(event3 = if_else(time_3 >= 5 & event3 == 1, 0, event3), 
         time_3 = if_else(time_3 >= 5, 5, time_3))

df_analysis <- df_analysis %>% 
  mutate(event = if_else(time >= 5 & event == 1, 0, event), 
         time = if_else(time >= 5, 5, time))



```



### Summary of the Study Population

```{r}
(t_1 <- df_analysis %>% 
  distinct(id, group, female, ethnicity, riskgroup, nadir_cd4, log_max_rna) %>% 
  select(-id) %>% 
  labelled::set_variable_labels(
    female = "Female sex",
    ethnicity = "Ethnicity",
    riskgroup = "HIV transmission group",
    log_max_rna = "Pretreatment HIV viral load, log cp/mL (IQR)",
    nadir_cd4 = "Nadir CD4 count, cells/µL (IQR)"
  ) %>% 
  tbl_summary(by = group) %>% 
  add_p())

gt::gtsave(as_gt(t_1), here::here("tables", "06-patient_characteristics_distinct.png"))



(t_2 <- df_analysis %>% 
  select(group, female, ethnicity, age, riskgroup, log_max_rna, 
       nadir_cd4, days_suppressed_actual, time_good_adh_actual, adherence_locf, 
       egfr, history_VF, nrti_mono, n_conmeds) %>% 
  mutate(across(c(days_suppressed_actual, time_good_adh_actual), ~.x/365.25)) %>% 
  labelled::set_variable_labels(
    female = "Female sex",
    ethnicity = "Ethnicity",
    age = "Age at trial start, years (IQR)",
    riskgroup = "HIV transmission group",
    log_max_rna = "Pretreatment HIV viral load, log cp/mL (IQR)",
    nadir_cd4 = "Nadir CD4 count, cells/µL (IQR)",
    days_suppressed_actual = "Time with HIV <50 cp/mL, years (IQR)",
    time_good_adh_actual = "Time with good adherence, years (IQR)",
    adherence_locf = "Missed dose in the last 4 weeks",
    egfr = "eGFR at trial start, ml/min (IQR)",
    history_VF = "History of virological failure", 
    nrti_mono = "History of single/dual NRTI therapy",
    n_conmeds = "Nr. of non-HIV drugs"
  ) %>%
  tbl_summary(by = group, 
              digits = all_continuous() ~ 1) %>% 
  add_p() %>% 
  bold_labels())

gt::gtsave(as_gt(t_2), here::here("tables", "06-patient_characteristics_alltrials.png"))


df_analysis %>% 
  group_by(id) %>% 
  summarise(trials = max(trial_nr)) %>% 
  summarise(median_trial = median(trials), 
            p25_trials = quantile(trials, 0.25), 
            p75_trials = quantile(trials, 0.75))
```


```{r}
df_analysis %>% 
  filter(group == "Switch") %>% 
  count(treatment, sort = TRUE) %>% 
  knitr::kable()

df_analysis %>% 
  filter(group == "Current") %>% 
  mutate(treatment = fct_lump(treatment, n = 10)) %>% 
  count(treatment, sort = TRUE) %>% 
  knitr::kable()
```


### Definition of Outcome

I decided to take 2 distinct outcomes:

1)  Time to confirmed virological failure, defined as **2 consecutive HIV viral loads \> 200 copies/mL** (FAILURE 1) or **1 viral load \> 200 copies/mL followed by a treatment change** (FAILURE 2)
2)  **Time to any HIV viral load above 200 copies/mL** (FAILURE 3)



### Any HIV viral load above 200 cp7mL

```{r unadjusted_event3}
# event 1/0 includes only failure 1 and 2
df_analysis_3 %>% 
  count(event, event_type)


# event 1/0 includes only failure 1 and 2
df_analysis %>% 
  count(event3, event_type)


# Kaplan Meier Plot -------------------------------------------------------
p <- ggsurvplot(fit = survfit(Surv(time_3, event3) ~ group, data = df_analysis_3),
                ggtheme = theme_light(base_family = "Lato"),
                palette = paletteer_d(`"ggsci::default_jama"`),
                xlim = c(0, 5),
                risk.table = TRUE,
                legend = "right",
                legend.title = "",
                legend.labs = c("Boosted ART regimen", "Switch to INSTI-based regimen"),
                censor = FALSE,
                break.time.by = 1,
                fontsize = 3,
                size = 0.7,
                risk.table.title = "",
                xlab = "\nYears since Baseline",
                ylab = "Viral Failure\n",
                tables.y.text.col = FALSE,
                fun = "event",
                conf.int = FALSE
)

kaplan_p <- p$plot + 
  theme(panel.grid.minor = element_blank(),
        panel.grid.major = element_line(linetype = 1, color = "grey90", size = 0.1),
        legend.position = c(0.3, 0.8)) + 
  scale_y_continuous(labels = scales::percent_format(accuracy = 1))

kaplan_t <- p$table + 
  labs(y = NULL, subtitle = "Individuals at risk") +
  theme(panel.grid = element_blank())

kaplan_p / kaplan_t + 
  plot_layout(heights = c(5, 1)) &
  theme(
    panel.grid.minor.x = element_blank(),
    plot.title = element_text(
      face = "bold",
      margin = margin(b = 1.24, unit = "line")
    ),
    plot.subtitle = element_text(
      face = "bold",
      margin = margin(b = 1.24, unit = "line")
    ),
    axis.title.x = element_text(margin = margin(t = 1.24, unit = "line"))
  )


ggsave(here("graphs", "06-kaplan_meier.png"), 
       bg = "white", width = 7, height = 5, dpi = 300)
ggsave(here("graphs", "06-kaplan_meier.pdf"), 
       bg = "white", width = 7, height = 5, dpi = 300, device = cairo_pdf)
```


```{r weights_event3}
# Inverse Probability Weighting -------------------------------------------

df_analysis_3 <- df_analysis_3 %>% 
  mutate(log_max_rna = if_else(max_rna > 0, log(max_rna), 0),
         anyTAMS = if_else(TAMS_n > 0, TRUE, FALSE))

weights <- ipwpoint(exposure = group_numeric, 
                    family = "binomial", 
                    link = "logit", 
                    numerator = ~1, # Stabilized weights
                    denominator = ~adherence_locf + history_VF + n_conmeds + 
                                   M184VI + K65R + anyTAMS + log_max_rna, 
                    data = as.data.frame(df_analysis_3))

wt_summary <- summary(weights$ipw.weights)
 tibble(quantile = names(wt_summary), 
        weight = wt_summary) %>% 
  knitr::kable(digits = 3)


# # Trim weights at 1 and 99% (should I do this?)
# trims <-  quantile(weights$ipw.weights, probs = c(0.01, 0.99))
# weights$ipw.weights[weights$ipw.weights > trims[2]] <- as.numeric(trims[2])
# weights$ipw.weights[weights$ipw.weights < trims[1]] <- as.numeric(trims[1])


df_analysis_3$wts <- weights$ipw.weights


df_analysis_3 %>% 
  ggplot(aes(x = wts)) + 
  geom_density(aes(fill = group), alpha = 0.5) + 
  # scale_y_continuous(labels = scales::percent_format(accuracy = 1)) + 
  facet_wrap(~group, scales = "free_y") +
  theme(legend.position = "None") + 
  labs(x = "Weights", y = "Density") + 
  theme(panel.grid = element_blank()) + 
  scale_x_continuous(limits = c(-1, 4)) +
  scale_fill_paletteer_d("awtools::mpalette")
  
# Survey Design for event 3 ------------------------------------------------------
svy_design <- svydesign(id = ~1, weights = ~wts, data = df_analysis_3)

vars <- c("adherence_locf", "history_VF","n_conmeds", "M184VI","K65R", 
          "anyTAMS", "log_max_rna")

tabUnmatched <- CreateTableOne(vars = vars, 
                               strata = "group", data = df_analysis_3, test = FALSE)

tabWeighted <- svyCreateTableOne(vars = vars, strata = "group", 
                                 data = svy_design, test = FALSE)



dataPlot <- data.frame(variable   = rownames(ExtractSmd(tabUnmatched)),
                       Unweighted  = as.numeric(ExtractSmd(tabUnmatched)),
                       Weighted   = as.numeric(ExtractSmd(tabWeighted)))


dataPlot %>%
  pivot_longer(-variable) %>% 
  arrange(name, value) %>% 
  mutate(variable = fct_inorder(variable)) %>%
  ggplot(aes(y = value, x = variable)) + 
  geom_hline(yintercept = 0.1, linetype = 2, color = "grey70") +
  geom_point(aes(color = name)) +
  geom_line(aes(group = name, color =name)) + 
  coord_flip() +
  labs(x = "Variable", y = "SMD") + 
  scale_color_paletteer_d("ggsci::default_nejm") + 
  theme(panel.grid = element_blank()) + 
  labs(color = NULL) 



df_3_sub <- df_analysis_3 %>% 
  select(age, female, ethnicity, riskgroup, egfr, dplyr::all_of(vars), group, wts)

svy_sub_design <- svydesign(id = ~1, weights = ~wts, data = df_3_sub)


suppressMessages(tbl <- tbl_svysummary(svy_sub_design, by = "group") %>% 
  add_difference(everything() ~ "smd") %>% 
  modify_column_hide(c(ci, p.value)))

tbl
```


```{r adjusted_event3_table}
# Fit weighted model ------------------------------------------------------
svy_design <- svydesign(id = ~1, weights = ~wts, data = df_analysis_3)

m_cox3 <- svycoxph(Surv(time_3, event3) ~ group,  design=svy_design) 

m_cox3 %>% 
  tidy(exp = TRUE, conf.int = TRUE) %>% 
  select(term, adj.HR = estimate, conf.low, conf.high, p.value) %>% 
  mutate(p.value = scales::pvalue(p.value)) %>% 
  knitr::kable(digits = 2)
```


```{r adjusted_event3_survivalcurve}
mod_wght <- svykm(Surv(time_3, event3) ~ group, design=svy_design)

surv_curve <- tibble(time = c(mod_wght[[1]]$time, mod_wght[[2]]$time),
                     surv = 1-c(mod_wght[[1]]$surv, mod_wght[[2]]$surv), 
                     treatment = rep(c("Boosted ART regimen", "Switch to INSTI-based regimen"), 
                                     times =  c(length(mod_wght[[1]]$time), 
                                                length(mod_wght[[2]]$time))))

ad_p <- surv_curve %>% 
  ggplot(aes(x = time, y = surv)) + 
  geom_line(aes(color = treatment), size = 0.75) + 
  theme(panel.grid.minor = element_blank(),
        panel.grid.major = element_line(linetype = 1, color = "grey90", size = 0.1),
        legend.position = c(0.3, 0.8)) + 
  labs(color = NULL, 
       x = "Years since Baseline", 
       y = "Viral Failure", 
       subtitle = "Adjusted Survival Curve")

kaplan_p <- kaplan_p + labs(subtitle = "Unadjusted Survival Curve")

kaplan_p + ad_p + 
  scale_color_paletteer_d("ggsci::default_jama") & 
  theme(legend.position = c(0.4, 0.9), 
        plot.subtitle = element_text(hjust = 0.5)) & 
   scale_y_continuous(labels = scales::percent_format(accuracy = 1), 
                     limits = c(0, 0.18)) 

ggsave(here("graphs", "06-kaplan_adj_surv_any.png"), 
       dpi = 300, bg = "white", width = 10, height = 6)
```


```{r adjusted_event3_ipwmod}
glm(group_numeric ~adherence_locf + history_VF + n_conmeds + 
                                   M184VI + K65R + anyTAMS + log_max_rna, 
    family = "binomial", data = df_analysis_3) %>% 
  tidy(exp = TRUE, conf.int = TRUE) %>% 
  mutate(p.value = scales::pvalue(p.value)) %>% 
  select(term, estimate, conf.low, conf.high, p.value) %>% 
  knitr::kable(digits = 2)
```

```{r}
glm(group_numeric ~adherence_locf + history_VF + n_conmeds + 
                                   M184VI + K65R + anyTAMS + log_max_rna, 
    family = "binomial", data = df_analysis_3)



coxph(Surv(time_3, event3) ~ group + adherence_locf + history_VF + n_conmeds + 
                                   M184VI + K65R + anyTAMS + log_max_rna,  
      data = df_analysis_3) %>% 
  tidy(exp = TRUE, conf.int = TRUE) %>% 
  filter(term == "groupSwitch") %>% 
  select(term, adj.HR = estimate) %>% 
  knitr::kable(digits = 2)

# Calculate bootstrap confidence intervals
boot_function <- function(data, indices) {
  d <- data[indices, ]
  obj <- coxph(Surv(time_3, event3) ~ group + adherence_locf + history_VF + n_conmeds + 
                                   M184VI + K65R + anyTAMS + log_max_rna, data = d)
  broom::tidy(obj)$estimate[1]
} 

set.seed(1)
# b <- boot(df_analysis_3, boot_function, R = 500, parallel = "multicore", 
#           ncpus = 12)
# write_rds(b, here("processed", "06-bootstraps_cox_any_detection.rds"))

b <- pro_read("06-bootstraps_cox_any_detection.rds")

tibble("HR" = b$t0,
       "LCI" = quantile(b$t, 0.025)[[1]],
       "UCI" = quantile(b$t, 0.975)[[1]]) %>%
  mutate_all(~scales::comma(exp(.x), accuracy = 0.01))


coxph(Surv(time_3, event3) ~ group,  
      data = df_analysis_3) %>% 
  tidy(exp = TRUE, conf.int = TRUE) %>% 
  filter(term == "groupSwitch") %>% 
  select(term, adj.HR = estimate) %>% 
  knitr::kable(digits = 2)

# Calculate bootstrap confidence intervals
boot_function <- function(data, indices) {
  d <- data[indices, ]
  obj <- coxph(Surv(time_3, event3) ~ group, data = d)
  broom::tidy(obj)$estimate[1]
} 

set.seed(1)
# b <- boot(df_analysis_3, boot_function, R = 500, parallel = "multicore", 
#           ncpus = 12)
# write_rds(b, here("processed", "06-bootstraps_cox_ua_any_detection.rds"))

b <- pro_read("06-bootstraps_cox_ua_any_detection.rds")

tibble("HR" = b$t0,
       "LCI" = quantile(b$t, 0.025)[[1]],
       "UCI" = quantile(b$t, 0.975)[[1]]) %>%
  mutate_all(~scales::comma(exp(.x), accuracy = 0.01))

```

```{r}
df_analysis_3 %>% 
  group_by(group) %>% 
  summarise(events = sum(event3), 
            fup = sum(time_3)) %>% 
  mutate(incidence_rate = events/fup * 1000)
```


### Confirmed virological failure

```{r unadjusted_event}
# event 1/0 includes only failure 1 and 2
df_analysis %>% 
  count(event, event_type)



# Kaplan Meier Plot -------------------------------------------------------
p2 <- ggsurvplot(fit = survfit(Surv(time, event) ~ group, data = df_analysis),
                ggtheme = theme_light(base_family = "Lato"),
                palette = paletteer_d(`"ggsci::default_jama"`),
                xlim = c(0, 5),
                risk.table = TRUE,
                legend = "right",
                legend.title = "",
                legend.labs = c("Boosted ART regimen", "Switch to INSTI-based regimen"),
                censor = FALSE,
                break.time.by = 1,
                fontsize = 3,
                size = 0.7,
                risk.table.title = "",
                xlab = "\nYears since Baseline",
                ylab = "Viral Failure\n",
                tables.y.text.col = FALSE,
                fun = "event",
                conf.int = FALSE
)

kaplan_p2 <- p2$plot + 
  theme(panel.grid.minor = element_blank(),
        panel.grid.major = element_line(linetype = 1, color = "grey90", size = 0.1),
        legend.position = c(0.3, 0.8)) + 
  scale_y_continuous(labels = scales::percent_format(accuracy = 1))

kaplan_t2 <- p2$table + 
  labs(y = NULL, subtitle = "Individuals at risk") +
  theme(panel.grid = element_blank())

kaplan_p2 / kaplan_t2 + 
  plot_layout(heights = c(5, 1)) &
  theme(
    panel.grid.minor.x = element_blank(),
    plot.title = element_text(
      face = "bold",
      margin = margin(b = 1.24, unit = "line")
    ),
    plot.subtitle = element_text(
      face = "bold",
      margin = margin(b = 1.24, unit = "line")
    ),
    axis.title.x = element_text(margin = margin(t = 1.24, unit = "line"))
  )


ggsave(here("graphs", "06-kaplan_meier_conf_VF.png"), 
       bg = "white", width = 7, height = 5, dpi = 300)
ggsave(here("graphs", "06-kaplan_meier_conf_VF.pdf"), 
       bg = "white", width = 7, height = 5, dpi = 300, device = cairo_pdf)
```


```{r weights_event}
# Inverse Probability Weighting -------------------------------------------

df_analysis <- df_analysis %>% 
  mutate(log_max_rna = if_else(max_rna > 0, log(max_rna), 0),
         anyTAMS = if_else(TAMS_n > 0, TRUE, FALSE))

weights2 <- ipwpoint(exposure = group_numeric, 
                    family = "binomial", 
                    link = "logit", 
                    numerator = ~1, # Stabilized weights
                    denominator = ~adherence_locf + history_VF + n_conmeds + 
                                   M184VI + K65R + anyTAMS + log_max_rna, 
                    data = as.data.frame(df_analysis))

wt_summary2 <- summary(weights2$ipw.weights)
 tibble(quantile = names(wt_summary2), 
        weight = wt_summary2) %>% 
  knitr::kable(digits = 3)


# # Trim weights at 1 and 99% (should I do this?)
# trims <-  quantile(weights$ipw.weights, probs = c(0.01, 0.99))
# weights$ipw.weights[weights$ipw.weights > trims[2]] <- as.numeric(trims[2])
# weights$ipw.weights[weights$ipw.weights < trims[1]] <- as.numeric(trims[1])


df_analysis$wts <- weights2$ipw.weights


df_analysis %>% 
  ggplot(aes(x = wts)) + 
  geom_density(aes(fill = group), alpha = 0.5) + 
  # scale_y_continuous(labels = scales::percent_format(accuracy = 1)) + 
  facet_wrap(~group, scales = "free_y") + 
  theme(legend.position = "None") + 
  labs(x = "Weights", y = "Density") + 
  theme(panel.grid = element_blank()) + 
  scale_x_continuous(limits = c(-1, 4)) + 
  scale_fill_paletteer_d("awtools::mpalette")
  
# Survey Design for event 3 ------------------------------------------------------
svy_design2 <- svydesign(id = ~1, weights = ~wts, data = df_analysis)

vars <- c("adherence_locf", "history_VF","n_conmeds", "M184VI","K65R", 
          "anyTAMS", "log_max_rna")

tabUnmatched2 <- CreateTableOne(vars = vars, 
                               strata = "group", data = df_analysis, test = FALSE)

tabWeighted2 <- svyCreateTableOne(vars = vars, strata = "group", 
                                 data = svy_design2, test = FALSE)



dataPlot2 <- data.frame(variable   = rownames(ExtractSmd(tabUnmatched2)),
                       Unweighted  = as.numeric(ExtractSmd(tabUnmatched2)),
                       Weighted   = as.numeric(ExtractSmd(tabWeighted2)))


dataPlot2 %>%
  pivot_longer(-variable) %>% 
  arrange(name, value) %>% 
  mutate(variable = fct_inorder(variable)) %>%
  ggplot(aes(y = value, x = variable)) + 
  geom_hline(yintercept = 0.1, linetype = 2, color = "grey70") +
  geom_point(aes(color = name)) +
  geom_line(aes(group = name, color =name)) + 
  coord_flip() +
  labs(x = "Variable", y = "SMD") + 
  scale_color_paletteer_d("ggsci::default_nejm") + 
  theme(panel.grid = element_blank()) + 
  labs(color = NULL) 



df_sub <- df_analysis %>% 
  select(age, female, ethnicity, riskgroup, egfr, dplyr::all_of(vars), group, wts)

svy_sub_design2 <- svydesign(id = ~1, weights = ~wts, data = df_sub)


suppressMessages(tbl <- tbl_svysummary(svy_sub_design2, by = "group") %>% 
  add_difference(everything() ~ "smd") %>% 
  modify_column_hide(c(ci, p.value)))

tbl
```


```{r adjusted_event_table}
# Fit weighted model ------------------------------------------------------
svy_design2 <- svydesign(id = ~1, weights = ~wts, data = df_analysis)

m_cox2 <- svycoxph(Surv(time, event) ~ group,  design=svy_design2) 

m_cox2 %>% 
  tidy(exp = TRUE, conf.int = TRUE) %>% 
  select(term, adj.HR = estimate, conf.low, conf.high, p.value) %>% 
  mutate(p.value = scales::pvalue(p.value)) %>% 
  knitr::kable(digits = 2)
```


```{r adjusted_event_survivalcurve}
mod_wght2 <- svykm(Surv(time, event) ~ group, design=svy_design2)

surv_curve2 <- tibble(time = c(mod_wght2[[1]]$time, mod_wght2[[2]]$time),
                     surv = 1-c(mod_wght2[[1]]$surv, mod_wght2[[2]]$surv), 
                     treatment = rep(c("Boosted ART regimen", "Switch to INSTI-based regimen"), 
                                     times =  c(length(mod_wght2[[1]]$time), 
                                                length(mod_wght2[[2]]$time))))

ad_p2 <- surv_curve2 %>% 
  ggplot(aes(x = time, y = surv)) + 
  geom_line(aes(color = treatment), size = 0.75) + 
  theme(panel.grid.minor = element_blank(),
        panel.grid.major = element_line(linetype = 1, color = "grey90", size = 0.1),
        legend.position = c(0.3, 0.8)) + 
  labs(color = NULL, 
       x = "Years since Baseline", 
       y = "Viral Failure", 
       subtitle = "Adjusted Survival Curve")

kaplan_p2 <- kaplan_p2 + labs(subtitle = "Unadjusted Survival Curve")

kaplan_p2 + ad_p2 + 
  scale_color_paletteer_d("ggsci::default_jama") & 
  theme(legend.position = c(0.4, 0.9), 
        plot.subtitle = element_text(hjust = 0.5)) & 
   scale_y_continuous(labels = scales::percent_format(accuracy = 1), 
                     limits = c(0, 0.18)) 

ggsave(here("graphs", "06-kaplan_adj_surv_conf_VF.png"), 
       dpi = 300, bg = "white", width = 10, height = 6)
```

```{r}
# Calculate bootstrap confidence intervals
boot_function <- function(data, indices) {
  d <- data[indices, ]
  obj <- coxph(Surv(time, event) ~ group, data = d)
  broom::tidy(obj)$estimate[1]
} 

set.seed(1)
# b <- boot(df_analysis, boot_function, R = 500, parallel = "multicore",
#           ncpus = 12)
# write_rds(b, here("processed", "06-bootstraps_cox_ua_VF.rds"))

b <- pro_read("06-bootstraps_cox_ua_VF.rds")

tibble("HR" = b$t0,
       "LCI" = quantile(b$t, 0.025)[[1]],
       "UCI" = quantile(b$t, 0.975)[[1]]) %>%
  mutate_all(~scales::comma(exp(.x), accuracy = 0.01)) %>% 
  knitr::kable(caption = "Unadjusted Estimates for VF")

# Calculate bootstrap confidence intervals
boot_function <- function(data, indices) {
  d <- data[indices, ]
  obj <- coxph(Surv(time, event) ~ group + adherence_locf + history_VF + 
                 n_conmeds + M184VI + K65R + anyTAMS + log_max_rna, data = d)
  broom::tidy(obj)$estimate[1]
} 

set.seed(1)
# b <- boot(df_analysis, boot_function, R = 500, parallel = "multicore",
#           ncpus = 12)
# write_rds(b, here("processed", "06-bootstraps_cox_VF.rds"))

b <- pro_read("06-bootstraps_cox_VF.rds")

tibble("HR" = b$t0,
       "LCI" = quantile(b$t, 0.025)[[1]],
       "UCI" = quantile(b$t, 0.975)[[1]]) %>%
  mutate_all(~scales::comma(exp(.x), accuracy = 0.01)) %>% 
  knitr::kable(caption = "Conditional Estimates for VF")
```


```{r adjusted_event_ipwmodel}

glm(group_numeric ~ adherence_locf + history_VF + n_conmeds + 
                                   M184VI + K65R + anyTAMS + log_max_rna, 
    family = "binomial", data = df_analysis) %>% 
  tidy(exp = TRUE, conf.int = TRUE) %>% 
  mutate(p.value = scales::pvalue(p.value)) %>% 
  select(term, estimate, conf.low, conf.high, p.value) %>% 
  knitr::kable(digits = 2)
```

```{r}
df_analysis %>% 
  group_by(group) %>% 
  summarise(events = sum(event), 
            fup = sum(time)) %>% 
  mutate(incidence_rate = events/fup * 1000)
```


